---
title: "Weekly Lecturer Report"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    self_contained: true
    css: report_styles.css
params:
  lecturer_id: ""
  week_id:     ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 8, fig.height = 4, dpi = 120)
library(ggplot2)
library(dplyr)
library(knitr)
library(kableExtra)

ANALYTICS_HOME <- Sys.getenv("ANALYTICS_HOME", ".")
source(file.path(ANALYTICS_HOME, "config.R"))
source(file.path(ANALYTICS_HOME, "scripts", "utils.R"))
source(file.path(ANALYTICS_HOME, "analysis", "weekly_lecturer_analysis.R"))
source(file.path(ANALYTICS_HOME, "scripts", "fetch_data.R"))
source(file.path(ANALYTICS_HOME, "scripts", "fetch_alerts.R"))

lecturer_id <- params$lecturer_id
week_id     <- params$week_id

stats    <- weekly_lecturer_analysis(lecturer_id, week_id)
lecturer <- fetch_lecturer(lecturer_id)
wp       <- fetch_weekly_period(week_id)
alerts   <- fetch_open_alerts_for_lecturer(lecturer_id)

theme_report <- theme_minimal(base_size = 12) +
  theme(plot.title    = element_text(size = 13, face = "bold", colour = "#1E3A5F"),
        axis.text     = element_text(colour = "#555"),
        panel.grid.minor = element_blank())
```

<div class="report-header">
  <h2>`r lecturer$full_name`</h2>
  <p>Week `r wp$week_number` / `r wp$year` &nbsp;·&nbsp; `r wp$start_date` – `r wp$end_date`</p>
</div>

## Overview

```{r overview-table}
overview <- data.frame(
  Metric = c("Sessions This Week", "Total Students Present",
             "Avg Engagement Score", "Avg Concentration"),
  Value  = c(as.character(stats$n_sessions),
             as.character(stats$total_students),
             ifelse(is.na(stats$avg_engagement),    "N/A", sprintf("%.0f%%", stats$avg_engagement * 100)),
             ifelse(is.na(stats$avg_concentration), "N/A", sprintf("%.0f%%", stats$avg_concentration * 100)))
)
kable(overview, align = c("l","r")) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = FALSE)
```

## Session-by-Session Engagement

```{r session-engagement}
if (!is.null(stats$session_details) && nrow(stats$session_details) > 0) {
  sd <- stats$session_details %>%
    mutate(label = paste0(course_code, " – ",
                          format(as.POSIXct(actual_start), "%a %d %b")),
           avg_eng_pct = avg_eng * 100)

  ggplot(sd, aes(x = reorder(label, actual_start), y = avg_eng_pct, fill = avg_eng_pct)) +
    geom_col(show.legend = FALSE, width = 0.55) +
    geom_hline(yintercept = 60, linetype = "dashed", colour = "#E74C3C", alpha = 0.7) +
    scale_fill_gradient(low = "#E74C3C", high = "#27AE60", limits = c(0, 100)) +
    scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "%")) +
    labs(x = NULL, y = "Avg Engagement", title = "Engagement per Session") +
    theme_report +
    theme(axis.text.x = element_text(angle = 25, hjust = 1))
} else {
  cat("No session data available for this week.")
}
```

## Student Performance

```{r student-table}
student_eng <- with_connection(function(con) {
  tryCatch(
    dbGetQuery(con, sprintf("
      SELECT CONCAT(u.first_name,' ',u.last_name) AS student_name,
             ROUND(AVG(CASE WHEN ses.concentration='high'   THEN 85
                            WHEN ses.concentration='medium' THEN 55
                            WHEN ses.concentration='low'    THEN 25
                            ELSE 10 END), 1) AS avg_focus,
             COUNT(*) AS snapshots
        FROM student_emotion_snapshots ses
        JOIN users u ON u.id = ses.student_id
        JOIN lecture_sessions ls ON ls.id = ses.session_id
       WHERE ls.lecturer_id = '%s'
         AND ses.captured_at BETWEEN '%s 00:00:00' AND '%s 23:59:59'
       GROUP BY ses.student_id, u.first_name, u.last_name
       ORDER BY avg_focus DESC",
      con@ptr, lecturer_id,
      as.character(wp$start_date[1]),
      as.character(wp$end_date[1]))),
    error = function(e) data.frame()
  )
})

if (nrow(student_eng) > 0) {
  n_show <- min(5, nrow(student_eng))
  bind_rows(
    head(student_eng, n_show) %>% mutate(Group = "🏆 Top"),
    tail(student_eng, n_show) %>% mutate(Group = "⚠️ Needs Support")
  ) %>%
    select(Group, student_name, avg_focus) %>%
    rename(Student = student_name, `Avg Focus` = avg_focus) %>%
    kable(align = c("l","l","r")) %>%
    kable_styling(bootstrap_options = c("striped","hover"), full_width = FALSE) %>%
    pack_rows("Top Students", 1, n_show) %>%
    pack_rows("Students Needing Support", n_show + 1, n_show * 2)
} else {
  cat("No student focus data available for this week.")
}
```

## Alerts

```{r alerts-table}
if (!is.null(alerts) && nrow(alerts) > 0) {
  alerts %>%
    select(student_name, alert_type, severity, triggered_at) %>%
    rename(Student = student_name, Type = alert_type,
           Severity = severity, `Triggered At` = triggered_at) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped","hover"))
} else {
  cat("✅ No open alerts for this week.")
}
```

## Teaching Recommendations

```{r tips}
avg_eng <- stats$avg_engagement
tips <- character(0)

if (!is.na(avg_eng)) {
  if (avg_eng < 0.4)       tips <- c(tips, "⚡ Engagement is critically low — consider interactive polls or group activities.")
  else if (avg_eng < 0.65) tips <- c(tips, "📈 Moderate engagement — try varying lecture pacing with short Q&A breaks.")
  else                     tips <- c(tips, "✅ Great engagement this week — keep up the current approach!")
}
if (!is.null(alerts) && nrow(alerts) > 3) {
  tips <- c(tips, "🔔 Several alerts triggered — review at-risk students individually.")
}
if (length(tips) == 0) tips <- "No specific recommendations this week."
cat(paste(tips, collapse = "\n\n"))
```

---
*Generated by EduVision Analytics · `r format(Sys.time(), "%d %B %Y %H:%M")`*

<script>
window.addEventListener('load', function() {
  document.querySelector('.report-print-btn') &&
    document.querySelector('.report-print-btn').addEventListener('click', window.print);
});
</script>
