---
title: "My Session Report"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: false
    self_contained: true
params:
  student_id:   ""
  session_id:   ""
  student_name: "Student"
  course_name:  "Course"
  session_date: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 6.5, fig.height = 3.5)
library(ggplot2)
library(dplyr)
library(knitr)

student_id <- params$student_id
session_id <- params$session_id

ANALYTICS_HOME <- Sys.getenv("ANALYTICS_HOME", ".")
source(file.path(ANALYTICS_HOME, "config.R"))
source(file.path(ANALYTICS_HOME, "scripts", "utils.R"))

conn <- get_connection()

# ── Load student snapshot data for this session ─────────────────────────────
snaps <- dbGetQuery(conn, sprintf("
  SELECT ses.emotion, ses.concentration, ses.confidence_score, ses.captured_at
  FROM student_emotion_snapshots ses
  WHERE ses.student_id = '%s' AND ses.session_id = '%s'
  ORDER BY ses.captured_at
", student_id, session_id))

# ── Load stored summary (if already computed by compute_student_summaries.R) ─
summary_row <- dbGetQuery(conn, sprintf("
  SELECT avg_concentration, attentive_percentage, dominant_emotion,
         pct_happy, pct_sad, pct_angry, pct_confused, pct_neutral, pct_engaged,
         pct_distracted, overall_engagement, snapshot_count
  FROM student_lecture_summaries
  WHERE student_id = '%s' AND session_id = '%s'
  LIMIT 1
", student_id, session_id))

# ── Load attendance ─────────────────────────────────────────────────────────
attendance <- dbGetQuery(conn, sprintf("
  SELECT sa.status, sa.joined_at, sa.left_at,
         COUNT(el.id) AS exit_count,
         COALESCE(SUM(el.exit_duration_minutes), 0) AS total_away_mins
  FROM session_attendance sa
  LEFT JOIN session_exit_logs el
         ON el.session_id = sa.session_id AND el.student_id = sa.student_id
  WHERE sa.student_id = '%s' AND sa.session_id = '%s'
  GROUP BY sa.status, sa.joined_at, sa.left_at
  LIMIT 1
", student_id, session_id))

DBI::dbDisconnect(conn)

# ── Derive metrics ──────────────────────────────────────────────────────────
n <- nrow(snaps)
has_snaps <- n > 0

if (has_snaps && nrow(summary_row) == 0) {
  # Fall back to computing on-the-fly if the summary table hasn't been populated yet
  conc_score  <- dplyr::case_when(
    tolower(snaps$concentration) == "high"       ~ 85,
    tolower(snaps$concentration) == "medium"     ~ 55,
    tolower(snaps$concentration) == "low"        ~ 25,
    tolower(snaps$concentration) == "distracted" ~ 10,
    TRUE ~ NA_real_
  )
  avg_conc    <- mean(conc_score, na.rm = TRUE) / 100
  attentive   <- (tolower(snaps$concentration) %in% c("high", "medium")) |
                 (tolower(snaps$emotion) == "engaged")
  attentive_p <- mean(attentive, na.rm = TRUE)
  dom_emotion <- names(which.max(table(snaps$emotion)))
  emo_pcts    <- as.data.frame(prop.table(table(tolower(snaps$emotion))) * 100)
  conc_pcts   <- as.data.frame(prop.table(table(tolower(snaps$concentration))) * 100)
} else if (nrow(summary_row) > 0) {
  avg_conc    <- as.numeric(summary_row$avg_concentration[1])
  attentive_p <- as.numeric(summary_row$attentive_percentage[1])
  dom_emotion <- summary_row$dominant_emotion[1]
  emo_pcts    <- data.frame(
    Var1 = c("happy","sad","angry","confused","neutral","engaged"),
    Freq = c(summary_row$pct_happy, summary_row$pct_sad, summary_row$pct_angry,
             summary_row$pct_confused, summary_row$pct_neutral, summary_row$pct_engaged) * 100
  )
  conc_pcts   <- data.frame(
    Var1 = c("high","medium","low","distracted"),
    Freq = c(
      100 - summary_row$pct_distracted * 100 - summary_row$attentive_percentage * 100 * 0.5,
      summary_row$attentive_percentage * 100 * 0.5,
      summary_row$pct_distracted * 100 * 0.5,
      summary_row$pct_distracted * 100
    )
  )
  if (has_snaps) {
    conc_pcts <- as.data.frame(prop.table(table(tolower(snaps$concentration))) * 100)
    emo_pcts  <- as.data.frame(prop.table(table(tolower(snaps$emotion))) * 100)
  }
} else {
  avg_conc    <- NA; attentive_p <- NA; dom_emotion <- "N/A"
  emo_pcts    <- data.frame(Var1 = character(), Freq = numeric())
  conc_pcts   <- data.frame(Var1 = character(), Freq = numeric())
}

# ── Colour maps ─────────────────────────────────────────────────────────────
emotion_colors <- c(
  happy = "#10b981", engaged = "#3b82f6", neutral = "#94a3b8",
  confused = "#f59e0b", sad = "#8b5cf6", angry = "#ef4444",
  surprised = "#06b6d4", fearful = "#fb923c", disgusted = "#6366f1"
)
conc_colors <- c(high = "#10b981", medium = "#3b82f6",
                 low  = "#f59e0b", distracted = "#ef4444")
```

---

**Student:** `r params$student_name` &nbsp;&nbsp;|&nbsp;&nbsp; **Course:** `r params$course_name` &nbsp;&nbsp;|&nbsp;&nbsp; **Date:** `r params$session_date`

---

## Summary

```{r summary-table}
if (!is.na(avg_conc)) {
  kable(data.frame(
    Metric  = c("Average Concentration", "Attentiveness", "Dominant Emotion",
                "Total Snapshots", "Attendance Status"),
    Value   = c(
      sprintf("%.0f%%", avg_conc * 100),
      sprintf("%.0f%%", attentive_p * 100),
      tools::toTitleCase(dom_emotion),
      ifelse(has_snaps, as.character(n), "0"),
      ifelse(nrow(attendance) > 0, tools::toTitleCase(attendance$status[1]), "N/A")
    )
  ), align = c("l","r"))
} else {
  cat("No snapshot data was recorded for this student in this session.")
}
```

## Concentration Breakdown

```{r conc-chart}
if (nrow(conc_pcts) > 0 && sum(conc_pcts$Freq) > 0) {
  conc_pcts$Var1 <- factor(conc_pcts$Var1, levels = c("high","medium","low","distracted"))
  ggplot(conc_pcts[conc_pcts$Freq > 0, ],
         aes(x = reorder(Var1, -Freq), y = Freq, fill = Var1)) +
    geom_col(width = 0.55, show.legend = FALSE) +
    scale_fill_manual(values = conc_colors, na.value = "#94a3b8") +
    scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "%")) +
    labs(x = NULL, y = "% of session", title = "Time Spent at Each Concentration Level") +
    theme_minimal(base_size = 11) +
    theme(panel.grid.major.x = element_blank(),
          axis.text.x = element_text(size = 10, face = "bold"))
} else {
  cat("No concentration data available.")
}
```

## Emotion Distribution

```{r emo-chart}
if (nrow(emo_pcts) > 0 && sum(emo_pcts$Freq) > 0) {
  emo_plot <- emo_pcts[emo_pcts$Freq > 0, ]
  ggplot(emo_plot, aes(x = reorder(Var1, -Freq), y = Freq, fill = Var1)) +
    geom_col(width = 0.55, show.legend = FALSE) +
    scale_fill_manual(values = emotion_colors, na.value = "#94a3b8") +
    scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "%")) +
    labs(x = NULL, y = "% of session", title = "Emotion Distribution") +
    theme_minimal(base_size = 11) +
    theme(panel.grid.major.x = element_blank(),
          axis.text.x = element_text(size = 9, face = "bold"))
} else {
  cat("No emotion data available.")
}
```

## Concentration Over Time

```{r conc-timeline}
if (has_snaps && "concentration" %in% colnames(snaps)) {
  snaps$captured_at <- as.POSIXct(snaps$captured_at)
  snaps$conc_score  <- dplyr::case_when(
    tolower(snaps$concentration) == "high"       ~ 85,
    tolower(snaps$concentration) == "medium"     ~ 55,
    tolower(snaps$concentration) == "low"        ~ 25,
    tolower(snaps$concentration) == "distracted" ~ 10,
    TRUE ~ NA_real_
  )
  snaps$smooth_conc <- {
    x <- snaps$conc_score
    vapply(seq_along(x), function(i) mean(x[max(1, i-4):i], na.rm = TRUE), numeric(1))
  }

  ggplot(snaps, aes(x = captured_at)) +
    geom_line(aes(y = conc_score), colour = "#cbd5e1", linewidth = 0.5, alpha = 0.5) +
    geom_line(aes(y = smooth_conc), colour = "#3b82f6", linewidth = 1.2) +
    scale_y_continuous(limits = c(0, 100),
                       breaks = c(10, 25, 55, 85),
                       labels = c("Distracted","Low","Medium","High")) +
    labs(x = "Time", y = "Concentration",
         title = "Your Concentration Throughout the Session",
         subtitle = "Blue line = smoothed (5-snapshot rolling avg)") +
    theme_minimal(base_size = 11)
} else {
  cat("No timeline data available.")
}
```

## Attendance

```{r attendance-table}
if (nrow(attendance) > 0) {
  att_display <- data.frame(
    Field = c("Status", "Joined At", "Left At", "Times Left Room", "Total Away (min)"),
    Value = c(
      tools::toTitleCase(as.character(attendance$status[1])),
      ifelse(is.na(attendance$joined_at[1]),   "—", format(as.POSIXct(attendance$joined_at[1]),   "%H:%M")),
      ifelse(is.na(attendance$left_at[1]),     "—", format(as.POSIXct(attendance$left_at[1]),     "%H:%M")),
      as.character(attendance$exit_count[1]),
      as.character(round(attendance$total_away_mins[1], 1))
    )
  )
  kable(att_display, align = c("l","r"))
} else {
  cat("No attendance record found for this session.")
}
```

---

*This report was generated automatically by EduVision Analytics.*
*Data is based on facial recognition analysis and is for academic support purposes only.*
